Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Rephrasing

In order to achieve BPMN-to-Solidity compilation,~\cite{weber2016untrusted} also describes translation rules to transform BPMN elements to Solidity code.
In~\cite{banuelos2017optimized}, these translation rules are further optimized to reduce Ethereum transaction costs and runtime. %TODO is this correct?

@@

\subsection{Requirements}
% refer to presentation here
% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln

>>>>

In order to achieve BPMN-to-Solidity compilation,~\cite{weber2016untrusted} also describes translation rules to transform BPMN elements to Solidity code.
Further work~\cite{banuelos2017optimized} tries to optimize the translation process, in turn reducing Ethereum execution costs by reducing required space and operations.

@@

\subsection{Requirements}

Before presenting the system, want to give an overview of the functional and non-functional requirements it has to fulfill.

The system's purpose is to facilitate trusted communication and collaboration between untrusting partners.
Therefore, it must be possible to send messages between partners.
To ensure security and trust in the system, both partners need a way to verify the authenticity of a message.
Verification is only possible if the system keeps track of users and permissions, i.e., implements a form of role-based access control with a user-to-role and role-to-permission mapping.
User and permission data has to be accessible at runtime, so that the communicating partners can use it to check the authenticity of messages.
It should also be possible to modify this data at runtime, to accomodate for changes in the company structure.

In order to make this system feasible in a production environment, we also require it to be reusable, measurable and cheap.
This implies keeping the implementation small and modular, and keeping it general enough to be used with the processes of different participants.
Measurability is required for evaluation and monitoring.
Since all computation done by smart contracts comes with gas costs, we want to keep the cost of our implementation as low as possible.
